AP/PA Tables ITHIM Global

### 2023-10-04 summary_tables_PA_AP.Rmd
Index to columns in summary_tables_PA_AP. There were some errors that are now fixed

  # add scenario specific PM2.5 concentration levels 
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)

@@

co2_conc$Scenario <- new_scen_names

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # define columns of interests
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # find the number of columns
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names # assign new column names

@@

  # extract the mean mMET values and create dataframe
  td <- round(colMeans(io[[city]]$outcomes$mmets[,(n_col - scen_length):n_col], na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

cl$Scenario <- new_scen_names

@@

  # assign new scenario names to columns
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names

@@

  # add total PM concentration levels for each scenario
  summary2$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, 2)

@@

  # CO2
  # extract CO2 transport emissions for each scenario
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', 'CO2')
  td$Scenario <- new_scen_names

@@

  # assign new scenario names
  names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names

>>>>

  # add scenario specific PM2.5 concentration levels 
  ## Dan - TODO: This can be problematic because we are assuming that the order from "pm_conc_pp"
  ## is the same as in "scenario_pm". And maybe it is, but don't know if this will
  ## apply always.
  ## To fix it we have to export "scenario_pm" with names and here compare the order of
  ## both objects.
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)

@@

# Dan: here the order is different (bus before car)
# co2_conc$Scenario <- new_scen_names
co2_conc$Scenario <- sapply(co2_conc$Scenario, FUN = get_qualified_scen_name)

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # define columns of interests
  # names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names
  change_names <- which(grepl("_mmet", names(io[[cities[x]]]$outcomes$mmets), fixed = TRUE))
  names(io[[cities[x]]]$outcomes$mmets)[change_names] <- sapply(gsub("_mmet" , "", names(io[[cities[x]]]$outcomes$mmets)[change_names]), FUN = get_qualified_scen_name)

@@

  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # find the number of columns
  # names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names # assign new column names
  change_names <- which(grepl("_mmet", names(io[[cities[x]]]$outcomes$mmets), fixed = TRUE))
  names(io[[cities[x]]]$outcomes$mmets)[change_names] <- sapply(gsub("_mmet" , "", names(io[[cities[x]]]$outcomes$mmets)[change_names]), FUN = get_qualified_scen_name)

@@

  # extract the mean mMET values and create dataframe
  # Dan: we change mmets column names before
  # td <- round(colMeans(io[[city]]$outcomes$mmets[,(n_col - scen_length):n_col], na.rm = T), 1) %>%
  #   as.data.frame() %>% tibble::rownames_to_column()
  td <- round(colMeans(io[[city]]$outcomes$mmets[,new_scen_names], na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)

@@

# We dont need this anymore
# cl$Scenario <- new_scen_names

@@

  # assign new scenario names to columns
  # names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names
  change_names <- which(grepl("pm_conc_", names(io[[cities[x]]]$outcomes$pm_conc_pp), fixed = TRUE))
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[change_names] <- sapply(gsub("pm_conc_" , "", names(io[[cities[x]]]$outcomes$pm_conc_pp)[change_names]), FUN = get_qualified_scen_name)

@@

  # add total PM concentration levels for each scenario
  ## Dan - TODO: This can be problematic because we are assuming that the order from "pm_conc_pp"
  ## is the same as in "scenario_pm". And maybe it is, but don't know if this will
  ## apply always.
  ## To fix it we have to export "scenario_pm" with names and here compare the order of
  ## both objects.
  summary2$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, 2)

@@

  # CO2
  # extract CO2 transport emissions for each scenario
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', 'CO2')

  # Dan: here the order is different (bus before car)
  # td$Scenario <- new_scen_names
  td$Scenario <- sapply(td$Scenario, FUN = get_qualified_scen_name)

@@

  # assign new scenario names
  # Dan: This is not needed anymore
  # names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names
